Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-26 1607 - JMC for g2/Paper/JMC_dis.tex

Assuming the Burkhardt-Cottingham sum rule to be strictly valid, we obtain a strong constraint on the transversity function,
\begin{align}
   \int dx\, \frac{1}{x} h_1(x) = 0 \ .
\end{align}
Even if the BC sun rule is broken by a 
$J = 0$ fixed pole with non-polynomial residue, i.e., if $g_2$ integrates to a finite but non-zero number \cite{Jaffe:1996zw}), we obtain that $h_1(x)/x$ must be integrable. This entails a bound on the small $x$ behavior of the transversity,
\begin{align}
  h_1(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
\end{align}
This bound will be very useful, \eg, in transversity fits, where the data at small $x$ is as yet very limited.

>>>>

Assuming the Burkhardt-Cottingham sum rule to be strictly valid, we obtain a strong constraint on the transversity function,
\begin{align}
   \int dx\, \frac{1}{x} h_1(x) = 0 \ .
\label{eq:ABsumrule}
\end{align}
Even if the BC sun rule is broken by a 
$J = 0$ fixed pole with non-polynomial residue, i.e., if $g_2$ integrates to a finite but non-zero number \cite{Jaffe:1996zw}), we obtain that $h_1(x)/x$ must be integrable. This entails a bound on the small $x$ behavior of the transversity,
\begin{align}
  h_1(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
\label{eq:ABbound}
\end{align}
This bound will be very useful, \eg, in transversity fits, where the data at small $x$ is, as yet, very limited, and in general for proper extrapolations when calculating moments.

The first moment is the first in which a contribution from the pure twist-3 part of $g_2$ appears:
\begin{align}
  d_1 & = \frac12 \sum_q e_q^2 \bigg( 2 \tilde g_T^q[1] + \hat g_T^q[1]
    + \frac{2M_q-m_q}{\Lambda} h_1^q[1] \bigg)
\end{align}
where $h_1^q[1] = \int_0^1 \dx $ is the contribution of a quark $q$ to the tensor charge. In this case, the transevrsity contribution is a background to the extraction of teh poure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice \cite{Bhattacharya:2016zcn} or fitted \cite{Pavia15, others, reviews?}. Furthermore the new sum rule \eqref{eq:ABsumrule} and bound \eqref{eq:ABbound} promise to improve future transversity fits. What is less obvious is how to calculate $M_q-m_q$ from first principles, since this is related to the spectral function of the quark propagator. We will, however, discuss later perspectives on how to measure it. Therefore the pure twist-3 part can, in principle, be properly isolated.

The third moment is interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see \cite{Jaffe-lectures}, and interpreted as as the average color force experienced by the struck quark as it exits teh nucleon \cite{M.Burkardt}. As in the previous case, however, the transversity contribution needs to be subtracted:
\begin{align}
  d_2 & = \frac12 \sum_q e_q^2 \bigg( 3 \tilde g_T^q[2] + \hat g_T^q[2]
    + \frac{3M_q-m_q}{\Lambda} h_1^q[2] \bigg)
\end{align}
